---
title: "HPV Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document: 
    reference_docx: "../reports/template.docx"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, 
    output_dir = "../reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, ft.align = "left", warning = FALSE)
options(gtsummary.tbl_summary.percent_fun = 
          function(x) sprintf(x * 100, fmt='%#.1f'))
```


```{r}
library(scales)
library(tidyverse)
library(naniar)
library(janitor)
library(gtsummary)
library(flextable)
library(writexl)
```

```{r}
hpv_results <- read_rds("../data/results_hpv.rds")
```



```{r}
nsize <- nrow(hpv_results)
npeople <- hpv_results |> distinct(sample_id) |> nrow()
missid <- hpv_results |> filter(is.na(sample_id)) |> nrow()

ncols <- hpv_results |> ncol()
nrows <- hpv_results |> nrow()

```

```{r}
gentable <- function(data = hpv_results, variables) {
  

t1 <- data %>% 
  remove_empty(which = c("cols")) |> 
  select(any_of(variables)) %>% 
  tbl_summary( type = list(
               where(is.factor) ~ "categorical",
               where(is.numeric) ~ "continuous"),
               missing_text =  "Missing",
               digits = list(all_categorical() ~ c(0, 1)),
               #statistic = list(where(is.Date) ~ "{date_iq_range}"),
               
               ) %>% 
  bold_labels() 

 


t1 <-  t1 |> 
  modify_header(label = "**Variable**") %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_header(label = "**Variable**") |> 
  gtsummary::as_flex_table() %>%
  theme_box() %>% 
  align(i = 1, align = "center", part = "header") %>% 
  flextable::font(fontname = "Calibri", part = "all") %>%
  flextable::padding(padding = 1, part = "all") %>% 
  bold(part = "header") %>% 
  bg(bg = "gray", part = "header") 
  
  

t1

}

```


## Dimensionality

The results file has `r ncols` columns and `r nrows` rows. 

## Sample Size 
We have `r nsize` results from `r npeople` participants. We had  `r missid` results with missing sample id. We are hopeful that the results can be linked to the survey dataset perfectly. 


## Missing information


```{r}
miss_var_summary(hpv_results) |> 
  filter(n_miss>0) |> 
  flextable() |> 
    theme_box() |> 
    flextable::font(fontname = "Calibri", part = "all") %>%
    flextable::padding(padding = 1, part = "all") %>% 
    bold(part = "header") %>% 
    bg(bg = "gray", part = "header") |>
    autofit()
```



## Table


```{r}


variables <- names(hpv_results)

ex <- c("sample_id", "analysis_created_at_utc", "filename_s", "barcode_s", "ap_version", "instrument_id_s", "assay_result_target_code", "analysis_authorized_at_utc", "analysis_authorized_by", "target_1_wells", "target_2_wells", "target_1_plates", "target_2_plates", "analysis_external_reference")

variables <- setdiff(variables, ex)

#variables <- c("assay_result_target_code", "assay_result_target")


gentable(hpv_results, variables)
```


\newpage

## Detected Assay Results


```{r}
hpv_pos <- hpv_results |> 
  filter(assay_result == "Detected") |> 
  filter(assay_result_target != "TVag") |> 
  group_by(sample_id) |> 
  add_count(sample_id, name = "ngenotypes") |> 
  ungroup()


tvag_pos <- hpv_results |> 
  filter(assay_result == "Detected") |> 
  filter(assay_result_target == "TVag")



# Get the participants with Tvag only

tvag_pos <- tvag_pos |> 
  anti_join(hpv_pos, by = "sample_id") |> 
  mutate(comment = "Only TVag detected")



hpv_neg <- hpv_results |> 
  anti_join(hpv_pos, by = "sample_id") |> 
  anti_join(tvag_pos, by = "sample_id") |> 
  mutate(comment = "Neither TVag nor HPV not detected")


hpv_neg <- hpv_neg |> 
  distinct(sample_id, assay_result, .keep_all = TRUE)


hpv_pos_participants <- hpv_pos |> 
  distinct(sample_id, .keep_all = TRUE) |> 
  mutate(comment = paste("Had ", ngenotypes, " HPV genotypes"))


participants <- hpv_pos_participants |> 
  bind_rows(hpv_neg) |> 
  bind_rows(tvag_pos) |> 
  select(sample_id, comment, ngenotypes) |> 
  mutate(
    ngenotypes = ifelse(is.na(ngenotypes), 0, ngenotypes),
    hpv_detected = ifelse(ngenotypes >0, "Yes", "No"),
    hpv_detected = as.factor(hpv_detected)
         )


nhpv <- participants |> filter(hpv_detected == "Yes") |> nrow()
nparticipants <- nrow(participants)


prev <- round(nhpv/nparticipants*100, 1)

participants <- participants |> 
  arrange(sample_id)




gentypes <- hpv_results |> 
  filter(assay_result == "Detected") |> 
  filter(assay_result_target != "TVag") |> 
  group_by(sample_id) |> 
  summarise(assay_results = str_c(assay_result_target, collapse = ", ")) |> 
  ungroup()
  

participants <- participants |> 
  left_join(gentypes, by = "sample_id")




write_xlsx(participants, "../data/participants.xlsx")

```



The total number of participants with lab results were `r nparticipants`. Out these, we detected at least HPV genotype in `r nhpv` partipants. This represents `r prev`. 


## Genotype Distribution

```{r}



hpv_pos_participants <- hpv_pos_participants |> 
  mutate(ngenotypes = as.factor(ngenotypes))

attr(hpv_pos_participants[['ngenotypes']], 'label') <- "Number of HPV genotypes"


gentable(hpv_pos_participants, "ngenotypes")


```



Over half of the participants tested had a single HPV genotype.  The highest number of HPV genotypes detected was 7. 


```{r}
# 
# library(scales)
# 
# hpv_pos_participants |>
#   count(ngenotypes) |>
#   ggplot(aes(x = factor(ngenotypes), y = n)) +
#   geom_col(fill = "#2C7FB8", width = 0.7) +
#   geom_text(aes(label = n), vjust = -0.4, size = 3.5, color = "grey20") +
#   scale_y_continuous(
#     expand = expansion(mult = c(0, 0.1)),
#     labels = comma
#   ) +
#   labs(
#     title = "Distribution of HPV Genotypes ",
#     subtitle = "Number of genotypes detected among HPV-positive participants",
#     x = "Number of HPV genotypes",
#     y = "Number of participants"
#   ) +
#   theme_minimal(base_size = 13) +
#   theme(
#     plot.title = element_text(face = "bold", size = 12),
#     plot.subtitle = element_text(color = "grey40", margin = margin(b = 10)),
#     plot.caption = element_text(color = "grey50", size = 9, hjust = 1),
#     panel.grid.major.x = element_blank(),
#     panel.grid.minor = element_blank(),
#     axis.text = element_text(color = "grey20"),
#     axis.title.x = element_text(margin = margin(t = 8)),
#     axis.title.y = element_text(margin = margin(r = 8)),
#     plot.margin = margin(15, 20, 15, 15)
#   )



```

## HPV Distribution

We targeted __18__ HPV genotypes and detected  
We detected `r nrow(hpv_pos)` HPV genotypes. The graph below shows the distribution of all the genotypes detected. 

```{r}





hpv_pos |>
  mutate(assay_result_target = as.factor(assay_result_target)) |>
  count(assay_result_target) |>
  ggplot(aes(x = fct_reorder(assay_result_target, n), y = n)) +
  geom_col(fill = "#2C7FB8", width = 0.7) +
  geom_text(aes(label = n), hjust = -0.2, size = 3.5, color = "grey20") +
  coord_flip() +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.1)),
    labels = comma
  ) +
  labs(
    title = "Distribution of HPV genotypes",
    x = NULL,
    y = "Number of samples",
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(color = "grey40", margin = margin(b = 10)),
    plot.caption = element_text(color = "grey50", size = 9, hjust = 1),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "grey20"),
    axis.title.x = element_text(margin = margin(t = 8)),
    #plot.margin = margin(15, 20, 15, 15)
  )
  
```







