---
title: "Water Sanitation Study"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  word_document: 
    reference_docx: "../reports/template.docx"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, 
    output_dir = "../reports/")
  })
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, ft.align = "left", warning = FALSE)
options(gtsummary.tbl_summary.percent_fun = 
          function(x) sprintf(x * 100, fmt='%#.1f'))
```


```{r}
library(tidyverse)
library(janitor)
library(gtsummary)
library(flextable)
library(dmngt)
library(lubridate)
```



```{r functions}
gentable <- function(variables) {
  
  
t1 <- wash %>% 
  remove_empty(which = c("cols")) |> 
  select(any_of(variables)) %>% 
  tbl_summary( type = list(
               where(is.factor) ~ "categorical",
               where(is.numeric) ~ "continuous"),
               missing_text =  "Missing",
               digits = list(all_categorical() ~ c(0, 1)),
               #statistic = list(where(is.Date) ~ "{date_iq_range}"),
               
               ) %>% 
  bold_labels() %>%
  modify_header(label = "**Variable**") %>% 
  modify_footnote(everything() ~ NA) %>% 
  gtsummary::as_flex_table() %>%
  theme_box() %>% 
  align(i = 1, align = "center", part = "header") %>% 
  flextable::font(fontname = "Calibri", part = "all") %>%
  flextable::padding(padding = 1, part = "all") %>% 
  bold(part = "header") %>% 
  bg(bg = "gray", part = "header")


t1


}

```


```{r import}
wash <- read_rds("../data/wash_clean.rds")

```




```{r extract}
sample_size <- nrow(wash)
consented_n <- wash |> filter(consent == "Yes") |> nrow()
start_pilot <- format(min(wash$interview_date), "%d-%B-%Y")
endt_pilot <- format(max(wash$interview_date), "%d-%B-%Y")


```

# Preliminaries

We began the pilot phase of the study on `r start_pilot` and concluded on `r endt_pilot`. `r sample_size` women were available in the households for interview. Out of these `r consented_n` consented for the interview and agreed to be interviewed. 


```{r}


```


# Demograpic Details 

Below are the demographic details of the women that participated in pilot phase of the WASH study. 

```{r}
vars <- c("sd02_1","age", "hhold_income", "household_size", "sd09_3")


gentable(vars)

```

# WASH Components


```{r}
vars <- c( "wsp01", "wsp04",
          "wsp08", "wsp11")


gentable(vars)

```

## Test Results


```{r}
vars <- c("wqa01", "wqa02", "wqa03", "wqa04", "wqa05", "wqa06", "wqa07")


gentable(vars)

```


# Hygiene and Sexual Health


```{r}
vars <- c("wsr01", "wsr02", "wsr03", "wsr04", "wsr05", "wsr06", "wsr08", "wsr09")

gentable(vars)
```





