---
title: "WASH Study Data Checks"
author: "Moses Otieno"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document: 
    reference_docx: "../reports/template.docx"
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, 
    output_dir = "../reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, ft.align = "left", warning = FALSE)
options(gtsummary.tbl_summary.percent_fun = 
          function(x) sprintf(x * 100, fmt='%#.1f'))
```

```{r}
library(tidyverse)
library(janitor)
library(gtsummary)
library(flextable)
library(officer)
library(dmngt)
library(lubridate)
library(dlookr)
library(patchwork)
library(lubridate)
```



```{r}
gentable <- function(data = wash, variables) {
  
 
  
t1 <- data %>% 
  remove_empty(which = c("cols")) |> 
  select(any_of(variables)) %>% 
  tbl_summary( type = list(
               where(is.factor) ~ "categorical",
               where(is.numeric) ~ "continuous"),
               missing_text =  "Missing",
               digits = list(all_categorical() ~ c(0, 1)),
               #statistic = list(where(is.Date) ~ "{date_iq_range}"),
               
               ) %>% 
  bold_labels() 

 


t1 <-  t1 |> 
  modify_header(label = "**Variable**") %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_header(label = "**Variable**") |> 
  gtsummary::as_flex_table() %>%
  theme_box() %>% 
  align(i = 1, align = "center", part = "header") %>% 
  flextable::font(fontname = "Calibri", part = "all") %>%
  flextable::padding(padding = 1, part = "all") %>% 
  bold(part = "header") %>% 
  bg(bg = "gray", part = "header") 
  
  

t1

}

```



```{r}
wash <- read_rds("../data/wash_main_clean.rds")

wash_labels <- labels_keep(wash)


```




# Preliminaries

The following are my observations, points of clarification  and a skim through of the entire dataset. 


# Structure of Questionaire

## Sections

You divided the divided the questionnaire into sections that makes it easy to navigate. 


## Language Translations

We have good Dholuo translations that can be easily understood by Dholuo speakers. However I noticed we did not have Swahili translation-possibly because it is Luo dominated region. Wondering if we had a non-luo married in the region but still does not understand Luo but comfortable with Swahili. In future we can provide Swahili translation. 


## Questionnaire and Dataset

I noticed the questionnaire is not in sync with the dataset, particulaly naming of the variable. I will give 2 examples; 

- `SD09. What is your religion?`  - in the dataset
- `SD10. What is your religion?` - in the questionnaire 

- `Do you understand the study as it has been explained to you? Do you agree to participate in this study?` - Dataset 
- `Are you willing/able to participate?` - Questionnaire



## Data Export

When exporting the dataset, choose the option of exporting the variable names as opposed to variable label. The data manager will then use the data dictionary to label the variables. 


## Duplicated Questions

I noticed some duplicated questions with the same choice label. 

- `Q12. What is the **Main** source of cooking fuel in your household?/Other` - Column BM in the Dataset
- `Q12. What is the **Main** source of cooking fuel in your household?/Other` - Column BO in the dataset

- `Q12-1. What is the **Main** source of lighting for your household?/Other (specify)` - Column BV
- `Q12-1. What is the **Main** source of lighting for your household?/Other (specify)` - Column BW


## Two Questions in One

`Do you understand the study as it has been explained to you? Do you agree to participate in this study?`. Were they answering the first part or the second part? We can separate the two in future. 



## Duplcated Respondent ID

```{r}
wash |> 
  get_dupes(respondent_id) |> 
  select(respondent_id, consent, refusal, interviewer, interview_date) |> 
    flextable() |> 
    theme_box() |> 
    flextable::font(fontname = "Calibri", part = "all") %>%
    flextable::padding(padding = 1, part = "all") %>% 
    bold(part = "header") %>% 
    bg(bg = "gray", part = "header") |>
    autofit()


```


# EDA


## Part 1: Socio-Demographic Information


```{r}
wash <- wash |> 
  filter(consent == "Yes")



part1 <- wash |> 
  select(starts_with("sd")) |> 
  names()

exclude <- c("sd01_2", "sd01_3", "sd04_1", "sd05_1", "sd09_2_1", "sd06")
include <- c("hhold_income", "age")

part1 <- part1[!part1 %in% exclude]
part1 <- c(part1, include)

gentable(wash, part1)

```

## Part 2: Water Sources and Practices

```{r}
part2 <- wash |> 
  select(starts_with("wsp")) |> 
  names()

exclude <- c("wsp01_1")

part2 <- part2[!part2 %in% exclude]


gentable(wash, part2)
```



## Part 3: Sanitation Facilities and Practices

```{r}


```


## Part 6: WASH and Sexual-Reproductive Health Hygiene Practices (Sensitive Section)



```{r}


```












